Open Questions for Computer Science and Cheminformatics

### 2011-11-21 OpenQuestions.tex
Added in Joerges edits

Binary feature vectors are a common practice for chemical similarity searches. The typical process starts with 1. creating
binary substructure (or other feature vectors) \cite{citeulike:8530538}, 2. creating fixed-length binary vectors of typically
1024 bits for reducing space requirements and speeding up further similarity searches (by loosing some accuracy), 3. creating 
further pre-computations for speeding up threshold based similarity searches \cite{doi:10.1021/ci800076s}.\\
Still, if we are interested to employ dynamic changes in the similarity encodings, e.g. using only a set of binary features,
then previously done hashing or pre-computations might need to be redone efficiently on the fly. Finally, the major goal
is to employ similarity searches \cite{doi:10.1021/ci200235e} on a scale of multiple million entries and more optimizations and
benchmarking studies are urgently required, e.g. using GPUs
\cite{doi:10.1021/ci1004948}, optimizing pair-wise similarity calculations \cite{MINF:MINF201100050}.
%
\item \emph{Large-scale browsing of molecular property spaces, e.g. on scaffold level, side-effect-level, ...}.

>>>>

  Binary feature vectors are a common practice for chemical similarity
  searches. The typical process starts with 1. creating binary
  substructure (or other feature vectors) \cite{citeulike:8530538},
  2. creating fixed-length binary vectors of typically 1024 bits for
  reducing space requirements and speeding up further similarity
  searches (by loosing some accuracy), 3. creating further
  pre-computations for speeding up threshold based similarity searches
  \cite{doi:10.1021/ci800076s}.\\  Still, if we are interested to employ
  dynamic changes in the similarity encodings, e.g. using only a set
  of binary features, then previously done hashing or pre-computations
  might need to be redone efficiently on the fly. Finally, the major
  goal is to employ similarity searches \cite{doi:10.1021/ci200235e}
  on a scale of multiple million entries and more optimizations and
  benchmarking studies are urgently required, e.g. using GPUs
  \cite{doi:10.1021/ci1004948}, optimizing pair-wise similarity
  calculations \cite{MINF:MINF201100050}.
%

\item \emph{Large-scale browsing of molecular property spaces, e.g. on scaffold level, side-effect-level, ...}.
